Mechanising Recursion Schemes with Magic-Free Coq Extraction

### 2024-10-10 paper/paper.tex
more related work on fusion

In the context of Coq, Danvy explores the use of fold/unfold lemmas to mechanize
equational reasoning about recursive programs in the Coq proof
assistant~\cite{DANVY_2022}. By formalizing recursive program transformations,
fold-unfold lemmas enable optimizations like fusion by allowing programs to be
systematically simplified, eliminating intermediate structures.

>>>>

In the context of Coq, Danvy explains the use of fold/unfold lemmas to mechanize
equational reasoning about recursive programs in the Coq proof
assistant~\cite{DANVY_2022}. By formalizing recursive program transformations,
fold-unfold lemmas enable optimizations like fusion by allowing programs to be
systematically simplified, eliminating intermediate structures. Additionally, an
approach to deforestation called the worker/wrapper transformation~\cite{gill09}
was formalised and mechanised in Agda~\cite{SCULTHORPE_HUTTON_2014}.
